---
docname: Curriculum Vitae
name: |
  | \huge Gera Flores Sempertegui
profilepic: "foto.png"
position: |
  | \scriptsize Data Analytics | Data Science | Machine Learning | Business Intelligence
address: |
  | \normalfont\scriptsize\faMapMarker\hspace{0.1cm}{\scriptsize San Martin 590, Miraflores, Lima, Peru}
phone: (+51) 948425000
email: "gflores1092@gmail.com"
linkedin: gflores1092
github: gflores1092
aboutme: |
  | \normalfont{Professional with over 10 years of work experience in the e-commerce, technology and startup industries. Expertise in data analytics, data science, business intelligence and machine learning. Prepared for highly technical positions, able to work under pressure and with an startup based work ethic.}
##www: gflores1092.carrd.co
headcolor: 414141
output: 
  vitae::awesomecv:
    keep_tex: true
always_allow_html: yes
header-includes:
  - \usepackage{parskip}
  - \usepackage{ragged2e}
  - \usepackage{changepage}
  - \usepackage{setspace}
  - \definecolor{awesome}{HTML}{0066CC}
  - \definecolor{text}{HTML}{0066CC}
  - \usepackage{graphicx}
  - \newcommand{\profilepic}{\includegraphics[width=1.5cm,height=1.5cm,keepaspectratio]{foto.png}}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, warning=FALSE, message=FALSE)
library(vitae)
library(xtable)
library(tidyverse)
```

```{r}
# Select the language (English or Spanish)
lang <- "Remote"  # Change to "Spanish" for the Spanish version
```

```{r}

# Functions

#tabular function
tabular <- function(tbl,
                    digits = 0,
                    include.colnames = FALSE,
                    include.rownames = FALSE,
                    hline.after = NULL,
                    size = getOption("xtable.size", NULL),
                    add.to.row = getOption("xtable.add.to.row", NULL),
                    ...)
                    {
                      tbl <- tbl %>%
                             mutate_all(
                               ~ if_else(
                                    . == "\\tiny", 
                                    "\\vspace{-0.20cm}", 
                                   paste("\\vspace{0.025cm}\\parbox{18cm}{", ., "}")
                                        )
                                   )
                    
                      tbl %>%
                        xtable(digits = digits, ...) %>%
                        print(include.colnames = include.colnames,
                              include.rownames = FALSE,
                              hline.after = hline.after,
                              comment = FALSE,
                              latex.environments = NULL,
                              floating = FALSE,
                              size = size,
                              add.to.row = add.to.row,
                              sanitize.text.function = function(x) {x}
                        )
                    }

# section function
section_title <- "\\hspace{0.25cm}\\color{black}{\\Large\\faInfoCircle}\\hspace{0.25cm}\\section{" 

# title function
title <- function(text, link = "") {
  if (link != "") {
    return(paste0("\\href{", link, "}{\\normalsize\\textbf{", text, "}}\\hfill"))
  } else {
    return(paste0("\\normalsize\\textbf{", text, "}\\hfill"))
  }
}

# company function
company <- function(text) {
  paste0("\\footnotesize{", text, "}\\hfill")
}

# bullet function
bullet <- function(text) {
  paste0("\\raisebox{+0.2\\height}{\\tiny\\faCircle}\\hspace{0.15cm}\\small{", text, "}\\hfill")
}

# location function
location <- function(text) {
  paste0("\\hfill\\scriptsize\\faMapMarker\\hspace{0.10cm}\\emph{", text, "}\\hfill")
}

# calendar function
calendar <- function(text) {
  paste0("\\hfill\\scriptsize\\faCalendarCheckO\\hspace{0.05cm}", text, sep="")
}

# word function
word <- function(text) {
  paste0("\\hfill\\small{", text, "}")
}

# paragraph function
paragraph <- function(text) {
  paste0("\\small{", text, "}\\hfill")
}

```

```{r}

# Spanish

spanish_sections <- c(
                    "Resumen", 
                    "Experiencia", 
                    "Educación",
                    "Certificados",
                    "Habilidades",
                    "Información adicional"
                    )

# English

english_sections <- c(
                    "Summary", 
                    "Experience", 
                    "Education",
                    "Certifications",
                    "Skills",
                    "Interests"
                    )
# Remote

remote_sections <- c(
                    "Summary", 
                    "Experience", 
                    "Education",
                    "Certifications",
                    "Skills",
                    "Interests"
                    )

```

```{r}

# Spanish

spanish_summary <- c(
  "Líder ejecutiva con 10 años de trayectoria en los sectores de e-commerce, tecnología y startups. Destaco en áreas como operaciones, logística, marketing, finanzas y data science. Con habilidades analíticas avanzadas y alta capacidad para la toma de decisiones basadas en datos. Experiencia en liderazgo de equipos interfuncionales de hasta 30 personas. Preparada para asumir roles de alta dirección, con el compromiso de fomentar la innovación, crecimiento, excelencia y éxito empresarial."
)

# English

english_summary <- c(
  "Accomplished executive leader with 10 years of diverse experience in e-commerce, technology, and startups. Proficient in operations, logistics, marketing, finance and data science. Strong analytical skills, adept at data-driven decision-making and experienced in leading cross-functional teams of up to 25. Ready for senior management roles, poised to drive innovation, growth, excellence and business success."
)

# Remote

remote_summary <- c(
  "Profesional con 10 años de experiencia gestionando equipos de hasta 25 personas en áreas como data analytics, operaciones, logística y marketing en industrias como e-commerce, tecnología, telecomunicaciones y minería. Alta capacidad analítica, entusiasta sobre nuevas tecnologías y herramientas y generalmente autodidacta en habilidades técnicas. Amplia experiencia en manejo de personas, con foco en el crecimiento personal, profesional y desarrollo de habilidades blandas."
)

```

```{r}

# Spanish

spanish_titles <- c(
                    "Head of Operations", 
                    "Logistics Performance Manager", 
                    "Growth Marketing Lead", 
                    "Analytics Lead"
                    )

spanish_companies <- c(
                      "FALABELLA.COM", 
                      "PEDIDOSYA", 
                      "GLOVO", 
                      "GLOVO"
                      )

spanish_bullets <- c(
  
  #[1]
  "Lideré un equipo de 30 personas responsable de la logística, analítica, finanzas y soporte comercial a clientes y sellers.",
  "Impulsé la experiencia al cliente y sellers (CSAT y NPS), aplicando estrategias centradas en la satisfacción y fidelización.",
  "Estandaricé y optimicé procesos operativos y comerciales de los marketplaces de Falabella, Tottus, Sodimac y Linio.",
  "Diseñé soluciones analíticas con Google Cloud para optimizar recursos y generar insights para la toma de decisiones.",
  "Lideré iniciativas comerciales, realizando capacitaciones y talleres presenciales y virtuales para eventos como Cyber Days.",
  "Fomenté la colaboración y comunicación, logrando una relación estrecha y productiva con el equipo y stakeholders.",
  "Generé una cultura orientada a datos, aumentando la eficiencia operativa en 40\\% y mejorando la productividad.",
  
  #[2]
  "Lideré un equipo de 5 personas a cargo de la excelencia operativa y el soporte al cliente, socios y repartidores.",
  "Reformulé estrategias operativas para maximizar la eficiencia, reducir tiempos de entrega y optimizar los recursos.",
  "Desarrollé soluciones analíticas, modelos predictivos, automatizaciones y herramientas analíticas usando SQL, R y Python.",
  "Dirigí la implementación de modelos de Machine Learning para predecir la demanda y gestionar la disponibilidad de flota.",
  "Incrementé las entregas on-time en 30\\% mediante la optimización de predicción de la demanda, zonas de servicio y rutas.",
  
  #[3]
  "Lideré un equipo multifuncional a cargo de alianzas comerciales, adquisición y retención de clientes y análisis de churn.",
  "Ejecuté promociones y recomendaciones data-driven para aumentar la lealtad, reducir churn y adquirir nuevos clientes.",
  "Establecí y gestioné alianzas estratégicas para mejorar la visibilidad y alcance, impulsar el crecimiento y la expansión.",
  "Diseñé y ejecuté campañas específicas que impulsaron el aumento de los ingresos en 20\\% y del ticket promedio en 10\\%.",
  "Mejoré la UX mediante la optimización del customer journey, aumentando user engagement en 25\\% y conversión en 15\\%.",
  
  #[4]
  "Lideré un equipo de Data Analysts y especialistas en Business Intelligence para proponer y desarrollar iniciativas analíticas.",
  "Dirigí proyectos de data science en varias áreas para proporcionar información accionable y tomar decisiones efectivas.",
  "Lideré proyectos exitosos para detección de fraudes, monetización de datos, desarrollo de socios y expansión de ingresos.",
  "Diseñé y ejecuté estrategias de pricing dinámico basadas en demanda y distancias, aumentando los ingresos hasta un 10\\%."
  
)

# English

english_titles <- c(
                    "Head of Operations", 
                    "Logistics Performance Manager", 
                    "Growth Marketing Lead", 
                    "Analytics Lead"
                    )

english_companies <- c(
                      "FALABELLA.COM",
                      "PEDIDOSYA",
                      "GLOVO",
                      "GLOVO"
                      )

english_bullets <- c(
  
  #[1]
  "Manage and lead a diverse team of 30 professionals across logistics, inverse logistics, analytics, and finance.",
  "Oversee support ticket resolution for customers and sellers, ensuring good experience and timely responses.",
  "Monitor and improve Customer Satisfaction (CSAT) and Net Promoter Score (NPS) for both customers and sellers.",
  "Leverage data, tools and Google Cloud Platform (GCP), to optimize processes, reduce costs, and improve efficiency.",
  "Led data-driven strategies, boosting operational efficiency up to 40\\%, reducing times, costs and enhancing productivity.",
  "Implemented a company-wide shift towards data-driven decision-making, using GCP's features to drive strategic insights.",
  
  #[2]
  "Led a team of 5 professionals in charge of operational excellence and customer, partner and rider support.",
  "Monitor and fine-tune operational parameters to maximize efficiency, reduce delivery times and optimize resources.",
  "Leverage SQL, R and Python to create data-driven solutions, automate processes and develop reporting and analysis tools.",
  "Oversaw data analytics efforts and implemented machine learning algorithms to predict demand and rider availability.",
  "Increased on-time deliveries by 30\\% through improved demand forecasting and service zones and route optimization.",
  
  #[3]
  "Led a cross-functional team in charge of brand partnerships, customer acquisition and retention and churn analysis.",
  "Executed data-driven promotions and recommendations to increase loyalty, reduce churn and acquire new customers.",
  "Establish and manage strategic partnerships to enhance brand visibility and reach, drive growth and market expansion.",
  "Designed and executed targeted campaigns that drove revenue growth by 20\\% and increased the average ticket by 10\\%.",
  "Enhanced UX by optimizing the customer journey based on data, raising user engagement by 25\\% and conversion by 15\\%.",
  
  #[4]
  "Supervised a team of data analysts and business intelligence specialists to propose and build analytics initiatives.",
  "Oversaw data analytics projects across various departments to provide actionable insights and drive business decisions.",
  "Led successful data-driven projects for fraud detection, data monetization, partner development and revenue expansion.",
  "Designed and executed dynamic pricing strategies based on peak demand and distances, boosting revenue up to 10\\%."

)

# Remote

remote_titles <- c(
                    "Head of Operations",
                    "Logistics Performance Manager", 
                    "Growth Marketing Lead", 
                    "Analytics Lead"
                    )

remote_companies <- c(
                      "FALABELLA.COM", 
                      "PEDIDOSYA", 
                      "GLOVO", 
                      "GLOVO"
                      )

remote_bullets <- c(
  
  #[1]
  "Led an operational excellence team, achieving 25\\% operational efficiency through predictive models in Python.",
  "Increased CSAT by 20\\% and NPS by 15\\% with projects such as a Machine Learning recommendation system in Python.",
  "Standardized processes across marketplaces, reducing processing time by 30\\% using Apache Airflow and SQL.",
  "Developed Google Cloud, BigQuery, and TensorFlow solutions, cutting operational costs by 25\\% with real-time analytics.",
  "Improved orders planning and delivery time with a ML classification system for product sizes with TensorFlow.",
  "Enhanced team collaboration with automated R and Python reporting, improving project delivery time by 15\\%.",
  "Integrated data-driven operations with Shiny dashboards, increasing efficiency by 40\\% and productivity by 50\\%.",
  
  #[2]
  "Increased on-time deliveries by 30\\% with optimized demand prediction models in SQL and Python.",
  "Reformulated strategies, reducing delivery times and optimizing resources with R and Python automations.",
  "Developed predictive models with TensorFlow and automations, improving fleet availability management by 25\\%.",
  "Implemented machine learning models for demand forecasting, enhancing resource allocation and efficiency.",
  "Optimized service areas and routes based on data, increasing delivery efficiency by 30\\% using Python.",
  
  #[3]
  "Responsible of customer acquisition and churn analysis, reducing churn by 20\\% with data-driven recommendations.",
  "Executed targeted campaigns, increasing revenue by 20\\% and average ticket size by 10\\% using predictive analytics.",
  "Established strategic partnerships, driving growth and expansion through data insights based on Market Basket Analysis.",
  "Improved UX and user engagement by 25\\%, optimizing the customer journey with advanced analytics.",
  "Boosted conversion rates by 15\\% with personalized marketing strategies and machine learning models.",
    
  #[4]
  "Led a team of Data Analysts and BI specialists, developing actionable insights through data science projects.",
  "Directed fraud detection and data monetization projects, reducing losses by 15\\% and increasing revenue by 20\\%.",
  "Implemented dynamic pricing strategies based on demand, increasing revenue by 10\\% with machine learning.",
  "Developed real-time analytical dashboards, improving decision-making efficiency by 30\\% using SQL and Python.",
  "Enhanced data-driven decision-making, optimizing operational and financial metrics through advanced analytics."
      
)
```

```{r}

# Spanish

spanish_degrees <- tribble(
  ~degree, ~start, ~end, ~institution, ~location,
  "Maestría en Administración de Negocios", 2018, 2018, "CENTRUM CATÓLICA", "Lima, Perú",
  "Programa en Administración de Negocios Globales", 2018, 2018, "MAASTRICHT UNIVERSITY", "Maastricht, Países Bajos",
  "Programa en Administración de Negocios Globales", 2018, 2018, "UNIVERSITY OF VICTORIA", "Victoria, B.C., Canadá",
  "Ingeniería Industrial", 2014, 2014, "PONTIFICIA UNIVERSIDAD CATÓLICA DEL PERÚ", "Lima, Perú",
)

spanish_certifs <- tribble(
  ~degree, ~start, ~end, ~institution, ~location, ~link,
  "Google Data Analytics", 2021, 2021, "GOOGLE", "Online", "",
  "Google Project Management", 2021, 2021, "GOOGLE", "Online", "",
  "Especialización en Deep Learning", 2020, 2020, "DEEPLEARNING.AI", "Online", "",
  "Analítica de Negocios y Gestión de la Información", 2016, 2016, "CENTRUM CATOLICA", "Lima, Perú",""
)

spanish_skills <- tribble(~type, ~skill,
        "Idiomas", "Inglés, Español, Portugués",
        "Data Science / Machine Learning", "R, Python, SQL",
        "Diseño / Desarrollo Web", "HTML, CSS, Javascript, PHP, WordPress",
        "IDEs", "Visual Studio Code, RStudio, Google Colab, Jupyter Notebooks",
        "Herramientas colaborativas", "Google Docs, Trello, Asana, Slack, Teams",
        "Herramientas de visualización", "Looker, Tableau, Data Studio, Power BI",
        "Herramientas CRM / Soporte", "Salesforce, Freshdesk, Jira, Kustomer",
        "Cloud computing", "Google Cloud, Amazon Web Services, Azure",
        "Otros", "Docker, Git, Spark, Regex, LaTeX, Markdown, Visual Basic, DAX",
        "ERPs", "SAP, Oracle",
)

spanish_hobbies <- tribble(~description,
        "Siempre estoy con actitud positiva y optimista, me encanta transmitir energías positivas con las personas que me rodean.",
        "Participo en causas de Diversidad, Equidad e Inclusión (DEI) en el trabajo y comunidad por medio de liderazgo inclusivo.",
        "Me encanta viajar y conocer nuevas culturas, he tenido la oportunidad de visitar 25 países y vivir en el extranjero.",
        "Suelo caminar mucho con un promedio de 10 mil pasos diarios los últimos 18 meses y mantener una vida activa.",
        "Me fascina la historia, disfruto aprendiendo de eventos históricos, civilizaciones antiguas y visitar museos."
)

# English

english_degrees <- tribble(
  ~degree, ~start, ~end, ~institution, ~location,
  "Master in Business Administration", 2018, 2018, "CENTRUM CATOLICA", "Lima, Peru",
  "Program in Global Business Administration", 2018, 2018, "MAASTRICHT UNIVERSITY", "Maastricht, Netherlands",
  "Program in Global Business Administration", 2018, 2018, "UNIVERSITY OF VICTORIA", "Victoria, B.C., Canada",
  "Industrial Engineer", 2014, 2014, "PONTIFICIA UNIVERSIDAD CATOLICA DEL PERU", "Lima, Peru",
)

english_certifs <- tribble(
  ~degree, ~start, ~end, ~institution, ~location, ~link,
    "Google Data Analytics", 2021, 2021, "GOOGLE", "Online", "",
    "Google Project Management", 2021, 2021, "GOOGLE", "Online", "",
    "Deep Learning Specialization", 2020, 2020, "DEEPLEARNING.AI", "Online", "",
    "Data Management and Analytics", 2016, 2016, "CENTRUM CATOLICA", "Lima, Perú",""
)

english_skills <- tribble(~type, ~skill,
        "Languages", "English, Spanish, Portuguese",
        "Data Science / Machine Learning", "R, Python, SQL",
        "Web Design / Development", "HTML, CSS, Javascript, PHP, WordPress",
        "IDEs", "Visual Studio Code, RStudio, Google Colab, Jupyter Notebooks",
        "Collaborative tools", "Google Docs, Trello, Asana, Slack, Teams",
        "Visualization tools", "Looker, Tableau, Data Studio, Power BI",
        "CRM / Support tools", "Salesforce, Freshdesk, Jira, Kustomer",
        "Cloud computing", "Google Cloud, Amazon Web Services, Microsoft Azure",
        "Others", "Docker, Git, Spark, Regex, LaTeX, Markdown, Visual Basic, DAX",
        "ERPs", "SAP, Oracle",
)

english_hobbies <- tribble(~description,
        "I always maintain a positive and optimistic attitude, and I love to share positive energy with those around me.",
        "I participate in Diversity, Equity, and Inclusion (DEI) causes at work and in the community through inclusive leadership.",
        "I love to travel and experience new cultures, having had the opportunity to visit 25 countries and live abroad.",
        "I typically walk a lot, averaging 10,000 steps daily for the past 18 months, and I maintain an active lifestyle.",
        "I am fascinated by history and enjoy learning about historical events, ancient civilizations, and visiting museums."
)

# Remote

remote_degrees <- tribble(
  ~degree, ~start, ~end, ~institution, ~location,
  "Master in Business Administration", 2018, 2018, "CENTRUM CATOLICA", "Lima, Peru",
  "Program in Global Business Administration", 2018, 2018, "MAASTRICHT UNIVERSITY", "Maastricht, Netherlands",
  "Program in Global Business Administration", 2018, 2018, "UNIVERSITY OF VICTORIA", "Victoria, B.C., Canada",
  "Industrial Engineer", 2014, 2014, "PONTIFICIA UNIVERSIDAD CATOLICA DEL PERU", "Lima, Peru",
)

remote_certifs <- tribble(
  ~degree, ~start, ~end, ~institution, ~location, ~link,
    "Google Data Analytics", 2021, 2021, "GOOGLE", "Online", "",
    "Google Project Management", 2021, 2021, "GOOGLE", "Online", "",
    "Deep Learning Specialization", 2020, 2020, "DEEPLEARNING.AI", "Online", "",
    "Data Management and Analytics", 2016, 2016, "CENTRUM CATOLICA", "Lima, Perú",""
)

remote_skills <- tribble(~type, ~skill,
        "Languages", "English, Spanish, Portuguese",
        "Data Science / Machine Learning", "SQL, R, Python (Keras / Tensorflow)",
        "Web Design / Development", "HTML, CSS, Javascript, PHP, WordPress",
        "IDEs", "Visual Studio Code, RStudio, Google Colab, Jupyter Notebooks",
        "Collaborative tools", "Google Docs, Trello, Asana, Slack, Teams",
        "Visualization tools", "Looker, Tableau, Data Studio, Power BI",
        "CRM / Support tools", "Salesforce, Freshdesk, Jira, Kustomer",
        "Cloud computing", "Google Cloud, Amazon Web Services, Microsoft Azure",
        "Others", "Docker, Git, Kubernetes, Airflow, Spark, Regex, LaTeX, Markdown, Visual Basic, DAX",
        "ERPs", "SAP, Oracle"
)

remote_hobbies <- tribble(~description,
        "I always maintain a positive and optimistic attitude, and I love to share positive energy with those around me.",
        "I participate in Diversity, Equity, and Inclusion (DEI) causes at work and in the community through inclusive leadership.",
        "I love to travel and experience new cultures, having had the opportunity to visit 25 countries and live abroad.",
        "I typically walk a lot, averaging 10,000 steps daily for the past 18 months, and I maintain an active lifestyle.",
        "I am fascinated by history and enjoy learning about historical events, ancient civilizations, and visiting museums."
)

```

```{r}
# Select the appropriate set of titles, companies, and bullets
if (lang == "English") {
    sections <- english_sections
    summary <- english_summary
    titles <- english_titles
    companies <- english_companies
    bullets <- english_bullets
    degrees <- english_degrees
    certifs <- english_certifs
    skills <- english_skills
    hobbies <- english_hobbies
  } else if (lang == "Spanish") {
    sections <- spanish_sections
    summary <- spanish_summary
    titles <- spanish_titles
    companies <- spanish_companies
    bullets <- spanish_bullets
    degrees <- spanish_degrees
    certifs <- spanish_certifs
    skills <- spanish_skills
    hobbies <- spanish_hobbies
  } else if (lang == "Remote") {
    sections <- remote_sections
    summary <- remote_summary
    titles <- remote_titles
    companies <- remote_companies
    bullets <- remote_bullets
    degrees <- remote_degrees
    certifs <- remote_certifs
    skills <- remote_skills
    hobbies <- remote_hobbies
  } else {
    stop("Language error.")
  }
```

\thispagestyle{empty}

\smallskip
<!--
\hspace{0.25cm}\color{black}{\Large\faInfoCircle}\hspace{0.25cm}\section{`r sections[1]`}

\vspace{0cm}

```{r summary, results='asis'}
tribble(~description,
        paragraph(summary[1]),
        "\\tiny"
        ) %>%
        tabular()
```

\vspace{0cm}
-->
\hspace{0.25cm}\color{black}{\Large\faBriefcase}\hspace{0.25cm}\section{`r sections[2]`}

\vspace{0cm}

```{r experience, results='asis'}
tribble(~position, ~start, ~end,

# Nota: Si hay error aquí es por los putos porcentajes        
        
        # Position
        title(titles[1]), 2021, NA,
        company(companies[1]), 2021, NA,
        bullet(bullets[1]), 2021, NA,
        bullet(bullets[2]), 2021, NA,
        bullet(bullets[3]), 2021, NA,
        bullet(bullets[4]), 2021, NA,
        bullet(bullets[5]), 2021, NA,
        bullet(bullets[6]), 2021, NA,
        bullet(bullets[7]), 2021, NA,
        "\\tiny", 2021, NA,

        # Position
        title(titles[2]), 2021, 2021,
        company(companies[2]), 2021, 2021,
        bullet(bullets[8]), 2021, 2021,
        bullet(bullets[9]), 2021, 2021,
        bullet(bullets[10]), 2021, 2021,
        bullet(bullets[11]), 2021, 2021,
        bullet(bullets[12]), 2021, 2021,
        "\\tiny", 2021, 2021,

        # Position
        title(titles[3]), 2020, 2021,
        company(companies[3]), 2020, 2021,
        bullet(bullets[13]), 2020, 2021,
        bullet(bullets[14]), 2020, 2021,
        bullet(bullets[15]), 2020, 2021,
        bullet(bullets[16]), 2020, 2021,
        bullet(bullets[17]), 2020, 2021,
        "\\tiny", 2020, 2021,

        # Position
        title(titles[4]), 2018, 2019,
        company(companies[4]), 2018, 2019,
        #bullet(bullets[17]), 2018, 2019,
        bullet(bullets[18]), 2018, 2019,
        bullet(bullets[19]), 2018, 2019,
        bullet(bullets[20]), 2018, 2019,
        bullet(bullets[21]), 2018, 2019,
        "\\tiny", 2018, 2019,
        
        ) %>%
        arrange(-start) %>%
        mutate(end = replace_na(as.character(end), "")) %>%
        mutate(years = if_else(end==start,
                                as.character(start),
                                paste(start, "--", end, sep=""))) %>%
        select(years, position) %>%
        group_by(years) %>%
        mutate(n = row_number()) %>%
        mutate(years = case_when(n>1 ~ "", TRUE ~ years)) %>%
        mutate(years = case_when(n==2 ~ location(degrees$location[1]), TRUE ~ years)) %>%
        mutate(aux = str_detect(years,'^20*')) %>%
        mutate(years = case_when(aux==TRUE ~ calendar(years), TRUE ~ years)) %>%
        select(position, years) %>%
        ungroup() %>%
        mutate(final=paste(position, years, sep="")) %>%
        select(final) %>%
        tabular()
```

\vspace{0cm}

\hspace{0.25cm}\color{black}{\Large\faGraduationCap}\hspace{0.25cm}\section{`r sections[3]`}

\vspace{0cm}

```{r education, results='asis'}
tribble(~degree, ~start, ~end,

        title(degrees$degree[1]), degrees$start[1], degrees$end[1],
        company(degrees$institution[1]), degrees$start[1], degrees$end[1],
        "\\tiny", degrees$start[1], degrees$end[1],

        title(degrees$degree[2]), degrees$start[2], degrees$end[2],
        company(degrees$institution[2]), degrees$start[2], degrees$end[2],
        company(degrees$institution[3]), degrees$start[3], degrees$end[3],
        "\\tiny", degrees$start[2], degrees$end[2],

        title(degrees$degree[4]), degrees$start[4], degrees$end[4],
        company(degrees$institution[4]), degrees$start[4], degrees$end[4],
        "\\tiny", degrees$start[4], degrees$end[4],

        ) %>%
        arrange(-start) %>%
        mutate(end = replace_na(as.character(end), "")) %>%
        mutate(years = if_else(end==start,
                                as.character(start),
                                paste(start, "--", end, sep=""),
                                paste(start, "--", end, sep="")
                                )) %>%
        select(years, degree) %>%
        mutate(r = case_when(grepl('textbf', degree) ~ row_number())) %>%
        fill(r, .direction = c('down')) %>%
        group_by(years, r) %>%
        mutate(n = row_number()) %>%
        mutate(years = case_when(n>1 ~ "", TRUE ~ years)) %>%
        mutate(years = case_when(
                    grepl(degrees$institution[1], degree) ~ location(degrees$location[1]),
                    grepl(degrees$institution[2], degree) ~ location(degrees$location[2]),
                    grepl(degrees$institution[3], degree) ~ location(degrees$location[3]),
                    grepl(degrees$institution[4], degree) ~ location(degrees$location[4]),
                    TRUE ~ years)) %>%
        mutate(aux = str_detect(years,'^20*')) %>%
        mutate(years = case_when(aux==TRUE ~ calendar(years), TRUE ~ years)) %>%
        select(degree, years) %>%
        ungroup() %>%
        mutate(final=paste(degree, years, sep="")) %>%
        select(final) %>%
        tabular()
```

\vspace{2cm}

\hspace{0.25cm}\color{black}{\Large\faUniversity}\hspace{0.25cm}\section{`r sections[4]`}

\vspace{0cm}

```{r certificates, results='asis'}
tribble(~degree, ~start, ~end,

        title(certifs$degree[1], certifs$link[1]), certifs$start[1], certifs$end[1],
        company(certifs$institution[1]), certifs$start[1], certifs$end[1],
        "\\tiny", certifs$start[1], certifs$end[1],

        title(certifs$degree[2], certifs$link[2]), certifs$start[2], certifs$end[2],
        company(certifs$institution[2]), certifs$start[2], certifs$end[2],
        "\\tiny", certifs$start[2], certifs$end[2],
        
        title(certifs$degree[3], certifs$link[3]), certifs$start[3], certifs$end[3],
        company(certifs$institution[3]), certifs$start[3], certifs$end[3],
        "\\tiny", certifs$start[3], certifs$end[3],

        title(certifs$degree[4], certifs$link[4]), certifs$start[4], certifs$end[4],
        company(certifs$institution[4]), certifs$start[4], certifs$end[4],
        "\\tiny", certifs$start[4], certifs$end[4],

        ) %>%
        arrange(-start) %>%
        mutate(end = replace_na(as.character(end), "")) %>%
        mutate(years = if_else(end==start,
                                as.character(start),
                                paste(start, "--", end, sep=""),
                                paste(start, "--", end, sep="")
                                )
               ) %>%
        select(years, degree) %>%
        group_by(years) %>%
        mutate(n = row_number()) %>%
        mutate(years = case_when(n %in% c(1,4) ~ years, TRUE ~ "")) %>%
        mutate(years = case_when(
                    grepl('DEEPLEARNING.AI|GOOGLE', degree) ~ location("Online"),
                    grepl('CENTRUM CATOLICA', degree) ~ location(degrees$location[1]),
                    TRUE ~ years
                   )
               ) %>%
        mutate(aux = str_detect(years, '^20*')) %>%
        mutate(years = case_when(aux==TRUE ~ calendar(years),
                                TRUE ~ years
                                )
               ) %>%
        select(degree, years) %>%
        ungroup() %>%
        mutate(final = paste(degree, years, sep="")) %>%
        select(final) %>%
        tabular()
```

\vspace{0cm}

\hspace{0.25cm}\color{black}{\Large\faBook}\hspace{0.25cm}\section{`r sections[5]`}

\vspace{0cm}

```{r skills, results='asis'}
tribble(~type, ~skill,
        title(skills$type[1]), word(skills$skill[1]),
        title(skills$type[2]), word(skills$skill[2]),
        title(skills$type[3]), word(skills$skill[3]),
        title(skills$type[4]), word(skills$skill[4]),
        title(skills$type[5]), word(skills$skill[5]),
        title(skills$type[6]), word(skills$skill[6]),
        title(skills$type[7]), word(skills$skill[7]),
        title(skills$type[8]), word(skills$skill[8]),
        title(skills$type[9]), word(skills$skill[9]),
        title(skills$type[10]), word(skills$skill[10]),
        "\\tiny", "\\tiny",
        ) %>%
        select(type, skill) %>%
        ungroup() %>%
        mutate(final = paste(type, skill, sep="")) %>%
        select(final) %>%
        tabular()
```

\vspace{0cm}

\hspace{0.25cm}\color{black}{\Large\faBalanceScale}\hspace{0.25cm}\section{`r sections[6]`}

\vspace{0cm}

```{r interests, results='asis'}
tribble(~hobbies,
        bullet(hobbies$description[1]),
        bullet(hobbies$description[2]),
        bullet(hobbies$description[3]),
        bullet(hobbies$description[4]),
        bullet(hobbies$description[5]),
        "\\tiny"
        ) %>%
        tabular()
```

\thispagestyle{empty}
